%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup of the document - size, style, languages

\documentclass[11pt,a4paper,twoside,openright,DIV=13,BCOR=1cm]{scrbook} % style of the document, fontsize, pagesize and spacing (incl. binding space)
\usepackage[english]{babel} % English document
\usepackage[utf8]{inputenc} % UTF-8 input
\usepackage[T1]{fontenc} % PDF language encoding
% \usepackage{a4} % Seitenrander Voreinstellung



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Mathematical symbols and numbering scheme for equations/figures/tables

\usepackage{amsmath} % align
\usepackage{amssymb} % \lesssim
\usepackage{braket} % for the bra-ket notation of QM
\numberwithin{equation}{chapter} % section based numbers in equations
\numberwithin{figure}{chapter} % figures
\numberwithin{table}{chapter} % and tables

% \usepackage{breqn} %automatic linebreaks in equations
% \usepackage{flexisym}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Settings for tables and captions

\usepackage{multirow} % enables multiple rows per column in tables
\usepackage[hang,small,bf]{caption} % bold captions + vertical alignment



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Importing graphics and allowing for multiple figures in a group

\usepackage{graphicx} % implements importing of graphics
\usepackage{subcaption} % allows for multiple figures next to each other
\captionsetup{compatibility=false}
% \usepackage{float} % allows for 'H' positioning of figures



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Importing formating of head and footlines, as well as the title pages

\usepackage{fancyhdr} % head and footline
\usepackage{titlesec} % gives control over titles in pages

\titleformat{\chapter}[display]      % titlesec
{\bf\Huge}               % {format}
{\chapapp~\thechapter }   % {label}
{1pc}                    % {separation}
{\thispagestyle{empty}}  % {before}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Actual formating head and footlines

% header and footer
\pagestyle{fancy}
\fancyhf{}

\setlength{\headheight}{15pt} %size of header
\fancyhead[LE,RO]{\slshape\thepage} % L - Left, E - Even page number, R - Right, O - Odd page number
\fancyhead[RE]{\slshape \leftmark}
\fancyhead[LO]{\slshape \rightmark}
% \fancyfoot[LO,LE]{\slshape Short Course on Asymptotics}
% \fancyfoot[C]{}
% \fancyfoot[RO,RE]{\slshape 7/15/2002}

\renewcommand{\headrulewidth}{0.5pt} % size of line in header
\renewcommand{\footrulewidth}{0pt} % size of line in footer


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Misc

\usepackage[figuresright]{rotating} % enables rotation of figures/tables
\usepackage{comment} % enables a comment environment
\usepackage{setspace} % enables individual line spacing
\usepackage[backend=biber,style=ieee,sorting=none]{biblatex} % use biblatex with biber
\addbibresource{bibliography.bib} % add the bibliography ressource

% self defined commands
\newcommand{\MET}{\mbox{$\not\hspace{-0.11cm}E_T$}} %missing transversal energy
\newcommand{\pct}{\scalebox{.9}{\%}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Setting up the pdf and allow for colored links

\usepackage[unicode]{hyperref} % Links
\usepackage[usenames,dvipsnames]{color} % for linkcolors
\hypersetup{plainpages=false,
  % bookmarks=true,         % show bookmarks bar?
  unicode=true,          % non-Latin characters in Acrobats bookmarks
  pdftoolbar=true,        % show Acrobats toolbar?
  pdfmenubar=true,        % show Acrobats menu?
  pdffitwindow=false,     % window fit to page when opened
  % pdfstartview={FitH},    % fits the width of the page to the window
  pdftitle={Masterthesis},    % title
  pdfauthor={Markus Radziej},     % author
  pdfsubject={Search for Resonant Slepton Production in a DiMuon + Jets Final State with 2012 CMS Data},   % subject of the document
  % pdfcreator={Creator},   % creator of the document
  % pdfproducer={Producer}, % producer of the document
  % pdfkeywords={keyword1} {key2} {key3}, % list of keywords
  % pdfnewwindow=true,      % links in new window
  % linktoc=page,               %only the page numbers are colored in the table of contents
  colorlinks=true,       % false: boxed links; true: colored links
  linkcolor=Maroon, % color of internal links
  citecolor=ForestGreen,        % color of links to bibliography
  filecolor=magenta,      % color of file links
  urlcolor=blue           % color of external links			
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Document starts here

\begin{document}
% ----------- titlepage --------------------
\pagenumbering{roman}
\pagestyle{empty}

\begin{titlepage}
  % \setcounter{page}{-5}
  \begin{center}
    \vspace{3.0cm}
    
    % Subject and university
    \rule{\linewidth}{0.5pt} \\
    \textsc{Master's thesis in physics} \\[0.4cm]
    
    % Title
    \doublespacing
    \textsc{\LARGE \textbf{Resonant Slepton Production in a DiMuon + Jets Final State at $\sqrt{s} = 8\,\text{TeV}$}}\\[1.5cm]
    \singlespacing
    
    % Author
    Written by\\[0.2cm]
    \textsc{Markus Radziej}\\
    
    
    \rule{\linewidth}{0.5pt} \\[3cm]
    
    
    
    % Submission to
    Submitted to the\\
    \textsc{\large Faculty of Mathematics, Computer Science and Natural Sciences}\\[1.5cm]
    Created at the\\
    \textsc{\large III. Phys. nInst. A} \\[0.2cm]
    of the\\
    \textsc{\large RWTH Aachen university} \\[0.5cm]
    
    Supervised by\\
    \textsc{Prof. Dr. Thomas Hebbeker}
    
    \vfill
    % Bottom of the page
    {\large \today}
    
  \end{center}
\end{titlepage}

\clearpage{\pagestyle{empty}\cleardoublepage} %empty page

% ------------- Declaration ---------------

\newpage
\noindent I assure that I have created this document independently, have not used any sources or aids other than the ones I have listed and have labeled quotes as such.\\[1.0cm]
\noindent Aachen the \hfill Signature

% ------------ Abstract - English ----------

\newpage
\begin{center} \textbf{Abstract} \end{center}
\noindent Presented is the search for resonant production of second generation sleptons in $R$-parity violating supersymmetry. It is performed using the $\mathcal{L} = 19.7\,\text{fb}^{-1}$ of proton-proton collisions recorded by the CMS experiment at the LHC, CERN during 2012. The centre-of-mass energy during this period was set to $\sqrt{s} = 8\,\text{TeV}$.

The underlying theory of supersymmetry is narrowed down to the cMSSM model, limiting the amount of free parameters to a manageable amount. As the commonly assumed $R$-parity is replaced by another, discrete symmetry called ``baryon triality'', additional parameters are available. By assuming single coupling dominance for the new lepton number violating Yukawa coupling $\lambda^\prime_{211}$, production of a single second generation slepton through two first generation quarks becomes possible. The decay signature of the slepton includes two muons and two jets, of which the lepton charges have the distinct possibility to be the same sign. This sets the final state apart from almost all Standard Model processes. Additionally, the amount of missing transverse energy is also quite low, as all particles of the final state can be fully reconstructed. Several analysis requirements are designed around exploiting these attributes to improve the ratio between signal and background by multiple orders of magnitude. A portion of the remaining backgrounds is replaced by a data-driven method to avoid dealing with hard to simulate multi-jet processes. Since no significant deviation of the data from the background prediction can be observed, limits are set on a wide range of the $m_0$-$m_{1/2}$ phase space. They both expand the parameter coverage and improve the limits with regards to the 2011 analysis predecessor by roughly a factor of 2.

%------------ Abstract - German ----------

\newpage
\begin{center} \textbf{Kurzdarstellung} \end{center}
\noindent Präsentiert ist die Suche nach resonanter Produktion von Sleptonen der zweiten Generation in $R$-Paritäts verletztender Supersymmetrie. Durchgeführt wurde sie mit $\mathcal{L} = 19.7\,\text{fb}^{-1}$ der Proton-Proton Kollisionen die vom CMS Experiment am LHC, CERN während 2012 aufgezeichnet wurden. Die Schwerpunktsenergie während dieser Periode betrug $\sqrt{s} = 8\,\text{TeV}$.

Die Theoriegrundlage der Supersymmetrie ist auf das cMSSM reduziert, was die Anzahl der freien Parameter auf eine überschaubare Größe limitiert. Die oftmals angenommene $R$-Parität ist durch eine andere diskrete Syemmtrie namens ``Baryon Trialität'' ersetzt, wodurch zusätzliche Parameter verfügbar sind. Durch die Annahme der alleinigen Dominanz der neuen Leptonenzahl verletzenden Yukawa-Kopplung $\lambda^\prime_{211}$, ist die Produktion eines Sleptons der zweiten Generation durch zwei Quarks der ersten Generation möglich. Die Zerfallssignatur des Sleptons schließt zwei Myonen und Jets mit ein, wobei die Ladungen der Leptonen die charakteristische Möglichkeit haben das selbe Vorzeichen zu tragen. Dies hebt den finalen Zustand von fast allen Standard Model Prozessen ab. Zusätzlich dazu ist die Menge an fehlender transversaler Energie sehr gering, da alle Teilchen des finalen Zustands vollständig rekonstruiert werden können. Mehrere Analysebedingungen werden erstellt um diese Eigenschaftungen auszunutzen, um das Verhältniss von Signal zu Untergrund um mehrere Größenordnungen zu verbessern. Ein Teil der verbleibenden Untergründe ist durch eine datengetriebene Methode ersetzt, um es zu vermeiden mit schwierig zu simulierenden Vielfach-Jet Prozessen zu arbeiten. Da keine signifikante Abweichung der Daten von der Untergrundvorhersage beobachtet werden kann, werden Grenzen auf einen großen Bereich des $m_0$-$m_{1/2}$ Phasenraums gesetzt. Diese erweitern die abgedeckten Paramterbereiche und verbessern die Grenzen in Hinsicht auf die 2011 Vorgängeranalyse um etwa einen Faktor 2.

% ------------ Tables --------------

\newpage
% \renewcommand{\contentsname}{Contents} 
\tableofcontents


% ----------- Document -------------


% introduction
\KOMAoptions{open=any}
\input{standardmodel} % note the page numbering and pagestyle are being set inside this include
\input{supersymmetry}
\input{experiment}

% analysis
\input{signature}
\input{datasets}
\input{objectsel}
\input{eventsel}
\input{datadrivenbg}
\input{systematics}
\input{results}

% appendices
\KOMAoptions{twoside=false}
\appendix
\input{mcsampleapp}
\input{n-1app}


% ----------- Bibliography -------------

\printbibliography[heading=bibintoc]
% \bibliographystyle{ieeetr}
% \bibliography{biblio}

\end{document}